People

### 2025-11-18 index.qmd
shortened welcome section and fixed paper link at bottom of home page

@@

[View all papers →](papers.qmd)

>>>>

## Welcome

Professor Bin Yu leads the Yu Group at UC Berkeley, a team of researchers in
Statistics and EECS focused on advancing statistical machine learning and
responsible data science. Her group develops interpretable methods and theory
for modern techniques such as random forests and deep learning, and applies them
to scientific domains including neuroscience, genomics, and precision medicine.

She is a member of the National Academy of Sciences and the American Academy of
Arts and Sciences, and delivered the 2023 IMS Wald Lectures and COPSS DAAL
Lecture. Her team created the PCS framework (predictability, computability, and
stability) to guide transparent and reliable data analysis.

@@

[View all papers →](papers/index.qmd)

### 2025-11-18 people/index.qmd
shortened welcome section and fixed paper link at bottom of home page

- Abhineet Agarwal (Ph.D. Student, Statistics)
- David Deriso (Ph.D. student, CS)
- Jakob Heiss (Post-doc)
- Yaxuan Huang (Ph.D. Student, Statistics)
- Nathan Benjamin McNaughton (MEng)
- Robin Netzorg (Ph.D. Student, CS)
- Anthony Ozerov (Ph.D. Student, Statistics)
- Zachary Rewolinski (Ph.D. Student, Statistics)
- Omer Ronen (Ph.D. Student, Statistics)
- Jingfeng Wu (Post-doc)
- Chengzhong Ye (Ph.D. Student, Statistics)
- Zeyu Yun (Ph.D. Student, CS)
- Austin Zane (Ph.D. Student, Statistics)

@@

>>>>

- David Deriso (Ph.D. Student, CS)
- Jakob Heiss (Post-doc)
- Hao Huang (MEng, EECS)
- Yaxuan Huang (Ph.D. Student, Statistics)
- Nathan Benjamin McNaughton (MEng, EECS)
- Robin Netzorg (Ph.D. Student, CS)
- Anthony Ozerov (Ph.D. Student, Statistics)
- Zachary Rewolinski (Ph.D. Student, Statistics)
- Omer Ronen (Ph.D. Student, Statistics)
- Jingfeng Wu (Post-doc)
- Chengzhong Ye (Ph.D. Student, Statistics)
- Zeyu Yun (Ph.D. Student, CS)
- Austin Zane (Ph.D. Student, Statistics)

@@

- Abhineet Agarwal (2025) - Technical Staff, Traversal
